Exploration

### 2018-03-14 exploration.Rmd
redundant object

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage objects & environmental covariates
p <- sp_i$p
sdd <- array(0, dim=dim(sdd.pr) + c(0,0,1,0)) # add layer for nEmig
sdd[,,1:2,] <- sdd.pr
n_z <- list(s=length(p$s_z), g=length(p$g_z),
            fl=length(p$fl_z), seed=length(p$seed_z))
n_x <- list(s=length(p$s_x), g=length(p$g_x),
            fl=length(p$fl_x), seed=length(p$seed_x))
X <- list(s=as.matrix(env.df[,1:n_x$s]), g=as.matrix(env.df[,1:n_x$g]),
          fl=as.matrix(env.df[,1:n_x$fl]), seed=as.matrix(env.df[,1:n_x$seed]))

>>>>

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage objects & environmental covariates
p <- sp_i$p
n_z <- list(s=length(p$s_z), g=length(p$g_z),
            fl=length(p$fl_z), seed=length(p$seed_z))
n_x <- list(s=length(p$s_x), g=length(p$g_x),
            fl=length(p$fl_x), seed=length(p$seed_x))
X <- list(s=as.matrix(env.df[,1:n_x$s]), g=as.matrix(env.df[,1:n_x$g]),
          fl=as.matrix(env.df[,1:n_x$fl]), seed=as.matrix(env.df[,1:n_x$seed]))
